Notes on filtration of logics containing {\bf K5}

### 2021-02-11 filtration-stuff/Text.tex
fix

\begin{defin}
  Let $\mathcal{L}$ be a normal modal logic and $\varphi \not\in \mathcal{L}$. A finite ``canonical'' model is a triple $\mathcal{M}_{\mathcal{L}}^{\varphi} = \langle W_{\mathcal{L}}^{\varphi}, R_{\mathcal{L}}^{\varphi}, \vartheta_{\mathcal{L}}^{\varphi} \rangle$, where
  \begin{enumerate}
    \item $W_{\mathcal{L}}^{\varphi}$ is the set all maximal theories that extend finite $\mathcal{L}$-theories
    \item $R_{\mathcal{L}}^{\varphi}$ is a relation such that
    $\langle W_{\mathcal{L}}^{\varphi}, R_{\mathcal{L}}^{\varphi} \rangle$ is an $\mathcal{L}$-frame
    and
    \begin{center}
    $\forall \Box \psi \operatorname{Sub}(\varphi) \:\:
    \forall \Delta_1 \in W_{\mathcal{L}}^{\varphi} \:\: (\Box \psi \in \Delta_1 \Leftrightarrow
    \forall \Delta_2 \in R_{\mathcal{L}}^{\varphi}(\Delta_1) \:\: \psi \in \Delta_2)$
    \end{center}
    \item $\vartheta_{\mathcal{L}}^{\varphi}(p) = \{ \Delta \in W_{\mathcal{L}}^{\varphi} \: | \: p \in \Delta \}$.
  \end{enumerate}
\end{defin}

@@

\begin{theorem} Let $\mathcal{L}$ be a complete normal modal logic, then the following are equivalent:
  \begin{enumerate}
    \item $\mathcal{L}$ admits strict filtrations
    \item If $\varphi \not\in \mathcal{L}$, then the finite ``canonical'' model $\mathcal{M}_{\mathcal{L}}^{\varphi}$ refutes $\varphi$
  \end{enumerate}
\end{theorem}

>>>>

\begin{defin}
  Let $\mathcal{L}$ be a normal modal logic and $\varphi \not\in \mathcal{L}$. A finite ``canonical'' model is a triple $\mathcal{M}_{\mathcal{L}}^{\varphi} = \langle W_{\mathcal{L}}^{\varphi}, R_{\mathcal{L}}^{\varphi}, \vartheta_{\mathcal{L}}^{\varphi} \rangle$, where
  \begin{enumerate}
    \item $W_{\mathcal{L}}^{\varphi}$ is the set all maximal theories that extend finite $\mathcal{L}$-theories
    \item $R_{\mathcal{L}}^{\varphi}$ is a relation such that
    $\langle W_{\mathcal{L}}^{\varphi}, R_{\mathcal{L}}^{\varphi} \rangle$ is an $\mathcal{L}$-frame
    and
    \begin{center}
    $\forall \Box \psi \in \operatorname{Sub}(\varphi) \:\:
    \forall \Delta_1 \in W_{\mathcal{L}}^{\varphi} \:\: (\Box \psi \in \Delta_1 \Leftrightarrow
    \forall \Delta_2 \in R_{\mathcal{L}}^{\varphi}(\Delta_1) \:\: \psi \in \Delta_2)$
    \end{center}
    \item $\vartheta_{\mathcal{L}}^{\varphi}(p) = \{ \Delta \in W_{\mathcal{L}}^{\varphi} \: | \: p \in \Delta \}$.
  \end{enumerate}
\end{defin}

@@

\begin{theorem} Let $\mathcal{L}$ be a complete normal modal logic, then the following are equivalent:
  \begin{enumerate}
    \item $\mathcal{L}$ admits strict filtrations
    \item If $\varphi \not\in \mathcal{L}$, there exists a finite ``canonical'' model $\mathcal{M}_{\mathcal{L}}^{\varphi}$ such that
    $\mathcal{M}_{\mathcal{L}}^{\varphi} \models \mathcal{L}$ and
    $\mathcal{M}_{\mathcal{L}}^{\varphi}$ refutes $\varphi$.
  \end{enumerate}
\end{theorem}
